Inefficient Concessions and Mediation

### 2020-02-21 draft.tex
clarify role of mediator

\begin{theorem}
	The strategy of not giving concessions in period 0, then playing Trust unless the other country defects to Fight is an equilibrium strategy for high types if $\delta_h \geq \frac{W}{(1-p)W + p(T + D)}$.
	\label{theorem:1}
\end{theorem}
\emph{Proof}: See appendix.
\\
In this equilibrium, two mutually distrustful countries go ahead and behave as if they trust anyway, taking a risk. This generally will happen when the result of trusting and then being betrayed is not catastrophic, or the odds of such a scenario are small. This is representative of a case where countries have suspicions about each other, but proceed anyway.

@@

Because many conflicts occur in an international arena with no clear enforceable rule of law (Waltz, 2002), much of the literature has focused on self-enforcing mechanisms. If however a credible third party does exist, then results beyond self enforcing agreements can be relevant.  A mediator with such enforcement ability is said to use manipulative mediation, specifically if she ``offered to verify compliance with the agreement''  or ``took responsibility for concessions''  (Bercovitch 1997). We will now introduce a mediator who does both.

>>>>

\begin{theorem}
	When low types give no concessions in period 0 and always play Fight thereafter, the strategy of not giving concessions in period 0, then playing Trust unless the other country defects to Fight is an equilibrium strategy for high types if $\delta_h \geq \frac{W}{(1-p)W + p(T + D)}$.
	\label{theorem:1}
\end{theorem}
\emph{Proof}: See appendix.
\\
In this equilibrium, two mutually distrustful countries go ahead and behave as if they trust anyway, taking a risk. This generally will happen when the result of trusting and then being betrayed is not catastrophic, or the odds of such a scenario are small. This is representative of a case where countries have suspicions about each other, but proceed anyway.

@@

Because many conflicts occur in an international arena with no clear enforceable rule of law (Waltz, 2002), much of the literature has focused on self-enforcing mechanisms. If however a credible third party does exist, then results beyond self enforcing agreements can be relevant.  A mediator with such enforcement ability is said to use manipulative mediation, specifically if she ``offered to verify compliance with the agreement''  or ``took responsibility for concessions''  (Bercovitch 1997). We will now introduce a mediator who does the latter.\footnote{Here the parties' actions in the stage game as well as their choices of whether to spend concessions on the civil versus the military sector are assumed to derive from their type, so there is no need for the mediator to enforce these decisions once the type is revealed. Thus, we do not assume that the mediator can do either because it is not necessary.}
